A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-08 doc/popl2013/evaluation.tex
Editting the evaluation section to be more precise about disjointness information

\subsubsection{Fluid Simulation}
\label{subsec:fluid}
Fluid is based on the {\tt fluidanimate} benchmark from the PARSEC 
suite\cite{bienia11benchmarking}.  Fluid simulates the flow of an incompressible fluid
using particles that move within a regular grid of cells.  To perform operations in 
parallel the cells are partitioned.  Unlike
Circuit, Fluid first creates regions and partitions them before
allocating cells in regions.  Another difference is that Fluid
maintains separate regions for ghost cells rather using multiple partitions of
the regions containing shared data.  Region relationships are again used to remember
the disjointness of information for the regions of each grid.

\subsubsection{Adaptive Mesh Refinement}
\label{subsec:amr}
The third application is an adaptive mesh refinement (AMR) benchmark 
from BoxLib \cite{BoxLib}.  The algorithm solves the two
dimensional heat diffusion equation on a grid of cells using three levels of refinement with subrefinements
randomly placed on the surface.  
%For each time step in the application, cells at the boundary of
%a refinement are interpolated from cells at a coarser level of refinement, energy fluxes between
%cells are computed, energy is transferred, and cells at a coarser level of refinement are restricted
%to the values of refined cells.  
The AMR application uses separate regions for every level of
refinement.  The regions at each level are partitioned several ways to provide multiple views of
the cells.  One partitioning separates cells into pieces that can be updated in
parallel.  Additional partitions are created for viewing data from coarser and finer levels of
the simulation.  Two types of region relationships are created: one for describing the pieces at 
each level of refinement, and another for describing the relationship between pieces at different
levels of refinement.  These region relationships capture both intra- and inter-level disjointness
information.  The dynamic nature of AMR requires that regions can be created and partitioned
at runtime.  
%The many ways in which cells are used also requires multiple simultaneous
%partitions of regions.

These applications show Legion is capable of 
expressing applications with both regular (Fluid,AMR) and irregular (Circuit) pointer data structures.
Being able to dynamically create and partition regions at runtime is crucial to Legion's
ability to handle applications that make runtime decisions about data organization(AMR).  Legion
is able to capture both allocate-then-partition (Circuit) and partition-then-allocate (Fluid) algorithms. 
Having multiple partitions of regions is necessary for describing the many ways 
that data can be accessed (Circuit,AMR).  All the types of privileges and coherence we have
described are needed in different combinations by the applications.  In
all applications, region relationships convey disjointness information.
% despite
%regions being a first-class feature that cannot be fully tracked statically.

>>>>

\subsubsection{Fluid Simulation}
\label{subsec:fluid}
Fluid is based on the {\tt fluidanimate} benchmark from the PARSEC 
suite\cite{bienia11benchmarking}.  Fluid simulates the flow of an incompressible fluid
using particles that move within a regular grid of cells.  To perform operations in 
parallel the cells are partitioned.  Unlike
Circuit, Fluid first creates regions and partitions them before
allocating cells in regions.  Another difference is that Fluid
maintains separate regions for ghost cells rather using multiple partitions of
the regions containing shared data.  Region relationships are used for remembering
which regions are required for each grid.

\subsubsection{Adaptive Mesh Refinement}
\label{subsec:amr}
The third application is an adaptive mesh refinement (AMR) benchmark 
from BoxLib \cite{BoxLib}.  The algorithm solves the two
dimensional heat diffusion equation on a grid of cells using three levels of refinement with subrefinements
randomly placed on the surface.  
%For each time step in the application, cells at the boundary of
%a refinement are interpolated from cells at a coarser level of refinement, energy fluxes between
%cells are computed, energy is transferred, and cells at a coarser level of refinement are restricted
%to the values of refined cells.  
The AMR application uses separate regions for every level of
refinement.  The regions at each level are partitioned several ways to provide multiple views of
the cells.  One partitioning separates cells into pieces that can be updated in
parallel.  Additional partitions are created for viewing data from coarser and finer levels of
the simulation.  Two types of region relationships are created: one for describing the pieces at 
each level of refinement, and another for describing the relationship between pieces at different
levels of refinement.  
%These region relationships capture both intra- and inter-level disjointness information.  
The dynamic nature of AMR requires that regions can be created and partitioned at runtime.  
%The many ways in which cells are used also requires multiple simultaneous
%partitions of regions.

These applications show Legion is capable of 
expressing applications with both regular (Fluid,AMR) and irregular (Circuit) pointer data structures.
Being able to dynamically create and partition regions at runtime is crucial to Legion's
ability to handle applications that make runtime decisions about data organization(AMR).  Legion
is able to capture both allocate-then-partition (Circuit) and partition-then-allocate (Fluid) algorithms. 
Having multiple partitions of regions is necessary for describing the many ways 
that data can be accessed (Circuit,AMR).  All the types of privileges and coherence we have
described are needed in different combinations by the applications.  Region relationships
are used in all applications. %, region relationships convey disjointness information.
% despite
%regions being a first-class feature that cannot be fully tracked statically.
